The complex network of trophic interactions in a subAntarctic oceanic Marine Protected Area

### 2023-07-17 MS_ToSubmit/MS_Burdwood_foodweb.Rmd
MEPS format

---
title: The complex network of trophic interactions in a subAntarctic oceanic Marine Protected
  Area
author:
  - name: Tomás I. Marina^a^
    email: tomasimarina@gmail.com
  - name: Irene R. Schloss^a^^,^^b^^,^^c^
  - name: Gustavo A. Lovrich^a^
  - name: Claudia C. Boy^a^
  - name: Daniel O. Bruno^a^^,^^c^
  - name: Fabiana L. Capitanio^d^^,^^e^
  - name: Sergio M. Delpiani^f^
  - name: Juan Martín Díaz de Astarloa^e^
  - name: Cintia Fraysse^a^
  - name: Virginia A. García Alonso^d^^,^^e^
  - name: Andrea Raya Rey^a^^,^^c^^,^^g^
  - name: Laura Schejter^h^
  - name: Mariela L. Spinelli^d^^,^^e^
  - name: Marcos Tatián^i^^,^^j^
  - name: Diego Urteaga^k^
  - name: Luciana Riccialdelli^a^

address:
  - code: 1
    address: Centro Austral de Investigaciones Cientificas (CADIC-CONICET), Argentina
  - code: 2
    address: Instituto Antartico Argentino (IAA), Argentina
  - code: 3
    address: Instituto de Ciencias Polares, Ambiente y Recursos Naturales (ICPA), Universidad de Tierra del Fuego (UNTDF), Argentina
  - code: 4
    address: Facultad de Ciencias Exactas y Naturales, Universidad de Buenos Aires (UBA), Argentina
  - code: 5
    address: Instituto de Biodiversidad y Biologia Experimental y Aplicada (IBBEA), Universidad de Buenos Aires-CONICET, Argentina
  - code: 6
    address: Instituto de Investigaciones Marinas y Costeras (IIMYC), Universidad Nacional de Mar del Plata-CONICET, Argentina
  - code: 7
    address: Wildlife Conservation Society, Argentina
  - code: 8
    address: Instituto Nacional de Investigacion y Desarrollo Pesquero (INIDEP), Consejo Nacional de Investigaciones Cientificas y Tecnicas (CONICET), Argentina
  - code: 9
    address: Facultad de Ciencias Exactas, Fisicas y Naturales, Universidad Nacional de Cordoba (UNC), Argentina
  - code: 10
    address: Instituto de Diversidad y Ecologia Animal (IDEA-CONICET)
  - code: 11
    address: Museo Argentino de Ciencias Naturales “Bernardino Rivadavia”, Argentina

abstract: |
  Globally, the total area of the world ocean designated under marine protection has increased in the recent decades. The majority of these Marine Protected Areas (MPAs) focus on the presence of particularly vulnerable, keystone, or charismatic species, large numbers of endemic species, and/or high biodiversity across taxonomic levels. In the sub-Antarctic region, the level of ocean protection is mainly associated to oceanic islands, except for the MPAs Namuncurá - Burdwood Bank I and II (MPA N-BB, ~53º–55ºS and ~56º–62ºW), which are associated to a submarine plateau and its southern adjacent deep slope region, respectively. Here, we present the first detailed analysis of the network of predator-prey interactions (food web) for the MPA N-BB ecosystem. We applied a network approach to characterise the food web in terms of complexity and structure, and identifying the species' role in such a framework. In terms of complexity, the MPA N-BB food web consisted of 1788 predator-prey interactions and 379 species, with a link density of 4.72 and a connectance of 0.01. In terms of structure, almost half of the consumers were omnivores (0.48), and the network displayed a small-world pattern. These findings suggest that the ecosystem might be vulnerable to external perturbations targeting highly connected species, although other properties might provide resilience and resistance, resulting in a rearranged structure that preserves its original functions. Furthermore, we identified several species as important in terms of different aspects of trophic structure and functioning, and response to perturbations. We suggest that generalist species, mainly fishes, play a crucial role in the ecosystem's bentho-pelagic coupling process and that other species, besides the longtail southern cod *Patagonotothen ramsayi* and the Fueguian sprat *Sprattus fuegensis*, should be considered as relevant energy transfers for the ecosystem. Finally, we argue that the diversity of species, including both the benthic and pelagic habitats, is responsible for seccuring the connectivity within the food web against perturbations, therefore contributing to the structure and stability of the ecosystem.

keywords: 
  - Food web
  - Complexity
  - Structure
  - Burdwood Bank
  - Southwest Atlantic
journal: "MEPS, Oikos, Ecological Applications, J of Applied Ecology (?)"
date: "`r Sys.Date()`"
classoption: preprint, 3p, authoryear
bibliography: AMPBancoBurdwood.bib
#nocite: '@*' cites all references in .bib file
linenumbers: true
numbersections: true
# Use a CSL with `citation_package = "default"`
csl: "apa.csl"
output: 
  rticles::elsevier_article:
    keep_tex: true
    citation_package: "default"
---

@@

# References

>>>>

---
title: The complex network of trophic interactions in a subAntarctic oceanic Marine Protected Area
author:
  - name: Tomás I. Marina^a^
    email: tomasimarina@gmail.com
    correspondingauthor: true
  - name: Irene R. Schloss^a^^,^^b^^,^^c^
  - name: Gustavo A. Lovrich^a^
  - name: Claudia C. Boy^a^
  - name: Daniel O. Bruno^a^^,^^c^
  - name: Fabiana L. Capitanio^d^^,^^e^
  - name: Sergio M. Delpiani^f^
  - name: Juan Martín Díaz de Astarloa^f^
  - name: Cintia Fraysse^a^
  - name: Virginia A. García Alonso^d^^,^^e^
  - name: Andrea Raya Rey^a^^,^^c^^,^^g^
  - name: Laura Schejter^h^
  - name: Mariela L. Spinelli^d^^,^^e^
  - name: Marcos Tatián^i^^,^^j^
  - name: Diego Urteaga^k^
  - name: Luciana Riccialdelli^a^

address:
  - code: 1
    address: Centro Austral de Investigaciones Científicas (CADIC-CONICET), Ushuaia, Argentina
  - code: 2
    address: Instituto Antártico Argentino (IAA), CABA, Argentina
  - code: 3
    address: Instituto de Ciencias Polares, Ambiente y Recursos Naturales (ICPA), Universidad de Tierra del Fuego (UNTDF), Ushuaia, Argentina
  - code: 4
    address: Facultad de Ciencias Exactas y Naturales, Universidad de Buenos Aires (UBA), CABA, Argentina
  - code: 5
    address: Instituto de Biodiversidad y Biología Experimental y Aplicada (IBBEA), Universidad de Buenos Aires-CONICET, CABA, Argentina
  - code: 6
    address: Instituto de Investigaciones Marinas y Costeras (IIMYC), Universidad Nacional de Mar del Plata-CONICET, Mar del Plata, Argentina
  - code: 7
    address: Wildlife Conservation Society, Argentina
  - code: 8
    address: Instituto Nacional de Investigación y Desarrollo Pesquero (INIDEP), Consejo Nacional de Investigaciones Científicas y Técnicas (CONICET), Mar del Plata, Argentina
  - code: 9
    address: Facultad de Ciencias Exactas, Físicas y Naturales, Universidad Nacional de Córdoba (UNC), Córdoba, Argentina
  - code: 10
    address: Instituto de Diversidad y Ecología Animal (IDEA-CONICET), Córdoba, Argentina
  - code: 11
    address: Museo Argentino de Ciencias Naturales “Bernardino Rivadavia”, CABA, Argentina
abstract: |
  Abstract: The total area of the world ocean designated under marine protection has increased recently. Most Marine Protected Areas (MPAs) target vulnerable, keystone, charismatic and or endemic species. In the sub-Antarctic, ocean protection is associated to oceanic islands,except for MPAs Namuncurá - Burdwood Bank I and II (MPA N-BB, ~53º–55ºS and ~56º–62ºW), which are associated to a submarine plateau and its southern adjacent deep slope, respectively. Here, we present the first analysis of the network of predator-prey interactions for the MPA N-BB. We applied a network approach to characterise the complexity and structure of the food web, and identify the species' role in such a framework. The MPA N-BB food web consisted of 1788 interactions and 379 species, with a connectance of 0.01. Almost half of the consumers were omnivores (0.48), and the network displayed a small-world pattern. These suggest that the ecosystem might be vulnerable to perturbations targeting highly connected species, although other properties might provide resilience and resistance, resulting in a rearranged structure that preserves its original functions. Several species arose as important in terms of different aspects of trophic structure and functioning, and response to perturbations. Generalist species, mainly fishes, play a crucial role in the ecosystem's benthopelagic coupling and should be considered as relevant energy transfers for the ecosystem. We argue that the diversity of species, including both the benthic and pelagic habitats, is responsible for securing the connectivity within the food web against perturbations, therefore contributing to the structure and stability of the ecosystem.
keywords: 
  - Food Web
  - Complexity
  - Structure
  - Burdwood Bank
  - Southwest Atlantic
classoption: preprint, 3p, authoryear
bibliography: AMPBancoBurdwood.bib
linenumbers: true
numbersections: true
# Use a CSL with `citation_package = "default"`
csl: "elsevier-harvard2.csl"
output: 
  rticles::elsevier_article:
    latex_engine: xelatex
    keep_tex: true
    citation_package: "default"
---

@@

# Literature Cited
